Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2024-10-09 index.Rmd
update index file

```{r message=FALSE, warning=FALSE, echo=TRUE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # whitout S-R
dir4<-here("s4") # 
dir5<-here("s5") # 
dir6<-here("s6") # 
dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
dir8<-here("s8") # s1 test data weigthing
dir9<-here("s9") # s1 w/ blocks
dirtest<-here("test")
Figs <- here("Figs")# S
```

@@

```{r eval=FALSE, message=F, include=FALSE}
#OR with rby separate
#shell(cmd="ss") # run SS to windows
# or 
r4ss::run(
  dir = dirtest,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)
```

@@

```{r}
df <- base.model1$lendbase

>>>>

```{r message=FALSE, warning=FALSE, echo=TRUE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # whitout S-R
dir4<-here("s4") # 
dir5<-here("s5") # 
dir6<-here("s6") # 
dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
dir8<-here("s8") # s1 platoons
dir9<-here("s9") # s1 w/ blocks
dirtest<-here("test")
Figs <- here("Figs")# S
```

@@

```{r eval=FALSE, message=F, include=FALSE}
#OR with rby separate
#shell(cmd="ss") # run SS to windows
# or 
r4ss::run(
  dir = dir8,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)
```

@@

```{r}
df <- base.modeltest$lendbase
